Response to the defense feedback

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection{New Implementation}
Recent work~\cite{bernstein2012security,libsodium} also proposes to design and implement clean-slate side-channel free software from scratch.

>>>>

\subsubsection{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl} also proposes to design and implement clean-slate side-channel free software from scratch.
